The watershed transform in ITK - discussion and new developments

### 2006-05-22 article/Article.tex
enhance floating type notes
darcs-hash:20060522113650-2fc9d-124aaded080255308f83d1473323b91d3f602a6a.gz

ITK watershed clearly produce a wrong segmentation in that case. However, using
a floating point image to store the distance map would have produce a better
result.
The segmentation of the morphological watershed is quite good, even if not perfect:
there are some curves in the separation line of the two labels. This is the
result of the distance approximation in the watershed algorithm.

>>>>

ITK watershed clearly produce a wrong segmentation in that case. However, using
a floating point image to store the distance map would have produce a better
result very similar to the one of the morphological watershed. It seems to be
another example of plateaus problem, where each level curve is seen as a plateau
when the pixel type of the distance image is an integral.

The segmentation of the morphological watershed is quite good, even if not perfect:
there are some curves in the separation line of the two labels. This is the
result of the distance approximation in the watershed algorithm.
